DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-06-30 ase2017/paper.tex
Editing Sec III

A graphical user interface application was developed (as shown in Fig.~\ref{fig:gui-for-tf}) 
to favor digital controller synthesis in MATLAB, besides improving usability and, 
consequently, attracting more digital dynamical system engineers. Users can provide all 
required parameters for digital controller synthesis: physical plant specification, 
fixed-point representation and dynamic inputs. 
%
\begin{figure}[ht]
    \centering
    \subfloat[Define the system representation and the physical plant.]{
		\includegraphics[width=0.2\textwidth]{step1.png}
		\label{step1}}
		\hfil
    \subfloat[Define implementation aspects and dynamic range.]{
	\includegraphics[width=0.2\textwidth]{step2.png}
		\label{step2}}
		\hfil
    \subfloat[Resulting digital controller synthesized by DSSynth.]{
	\includegraphics[width=0.2\textwidth]{step3.png}
		\label{step2}}
		\hfil
    \subfloat[Step response for the synthesized digital controller.]{
	\includegraphics[width=0.22\textwidth]{step4.png}
		\label{step3}}
		\hfil
    \caption{DSSynth GUI application for the controller synthesis based on transfer function representation.}
    \label{fig:gui-for-tf}
\end{figure}

>>>>

A graphical user interface application was developed (as shown in Fig.~\ref{fig:gui-for-tf}) 
to favor digital controller synthesis in MATLAB. Its aim is to improve usability and, 
consequently, to attract more digital dynamical system engineers. Users can provide all 
required parameters for digital controller synthesis: physical plant specification, 
fixed-point representation and dynamic inputs. 
%
\begin{figure}[ht]
    \centering
    \subfloat[Define the system representation and the physical plant.]{
		\includegraphics[width=0.2\textwidth]{step1.png}
		\label{step1}}
		\hfil
    \subfloat[Define implementation aspects and dynamic range.]{
	\includegraphics[width=0.2\textwidth]{step2.png}
		\label{step2}}
		\hfil
    \subfloat[Resulting digital controller synthesized by DSSynth.]{
	\includegraphics[width=0.2\textwidth]{step3.png}
		\label{step2}}
		\hfil
    \subfloat[Step response for the synthesized digital controller.]{
	\includegraphics[width=0.22\textwidth]{step4.png}
		\label{step3}}
		\hfil
    \caption{DSSynth GUI application for the controller synthesis based on transfer function representation.}
    \label{fig:gui-for-tf}
\end{figure}
